The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-21 paper.tex
update

The gamma-ray emission of the \textit{Fermi} bubbles is observed in the energy range\
of $1\lesssim E_{\gamma} \lesssim 100$ GeV and has an almost spatially uniform hard\
spectrum, sharp edges and an approximately flat brightness distribution.\

>>>>

The gamma-ray emission of the \textit{Fermi} bubbles is observed in the energy range\
of 1--100 GeV and has an almost spatially uniform hard\
spectrum, sharp edges and an approximately flat brightness distribution.\
